Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-01-15 chapters/chapter01.tex
working on the subsection on codon models

Spatial phylogenetic projections have already been utilized in the field \citep{Kidd2006,Parks2009}, yet most of these applications remain limited to mapping phylogenetic tip taxa to their geographical coordinates, without providing robust statistical estimates of the geographic locations at the ancestral nodes nor the measures of uncertainty in the inference.
Fortunately, the advent of powerful and flexible Geographic Information Systems (GIS) has fostered an interesting possibility to visualize both the spatial and temporal information resulting from viral phylogenetic analysis.
Presenting readily interpretable visual summaries of the inferences in e communicated to the researchers across different fields is one of the more important aspects of this thesis.

@@

@@

\begin{equation}  
q_{\beta}\left(\theta\right)=P\left(\mathbf{X}\mid\theta,M\right)\times P\left(\theta\mid M\right).
\label{eq:ss_ps}
\end{equation}

>>>>

Spatial phylogenetic projections have already been utilized in the field \citep{Kidd2006,Parks2009}, yet most of these applications remain limited to mapping phylogenetic tip taxa to their geographical coordinates, without providing robust statistical estimates of the geographic locations at the ancestral nodes nor the measures of uncertainty in the inference.
Fortunately, the advent of powerful and flexible Geographic Information Systems (GIS) has fostered an interesting possibility to visualize both the spatial and temporal information resulting from viral phylogenetic analysis.
Presenting readily interpretable visual summaries of the inferences that can be communicated to the researchers across different fields is one of the more important aspects of this thesis.

@@

\subsection{Codon models of evolution\label{sub:codon})
%TODO: briefly introduce, mg is later, show gy94

@@

\begin{equation}  
q_{\beta}\left(\theta\right)=P\left(\mathbf{X}\mid\theta,M\right)^{\beta} \times P\left(\theta\mid M\right).
\label{eq:ss_ps}
\end{equation}
